---
title: "Simple document"
output:
  html_document:
    toc: true
    toc_float: true
---

I'm an R Markdown document! 

# Section 0: libraries
```{r setup, message = F}
#eval = F has that code chunk not run when knitting the document
library(tidyverse)
```


# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

**word** --> bold
_word_ --> italics

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3: a tibble

```{r}
plot_df = 
  tibble(
    x = rnorm(1000, 0.5),
    y = 1 + 2 * x + rnorm(1000)
  )

head(plot_df)
```

# Section 4: plots

These are plots from our random sample 

```{r echo=F, message=F}
#echo = F hides the code chunks
#message = F hides the messages that come up when you run the code

#histogram
ggplot(plot_df, aes(x = x)) + geom_histogram()

#scatter plot
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```
# Section 5: Learning Assessment 2
Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean
1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then,
produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens
if you set eval = FALSE to the code chunk? What about echo = FALSE?

This plot shoes the distribution of the absolute value of $X \sim N(1, 1)$

```{r}
set.seed(0)

assessment_2 = tibble(
  num_var = rnorm(500, mean = 1),
  log_var = num_var > 0,
  abs_var = abs(num_var)
)

ggplot(assessment_2, aes(x = abs_var)) + geom_histogram()
```
The median is `r round(median(pull(assessment_2, abs_var)), 2)`.



He says not to use $. something about it being dangrous for accidentally changing the dataset. idk. (theory: just cuz we haven't learned it yet)

according to copilot: I think it's a good idea to avoid it (the dollar sign) for now. I think the $ is used to access a specific column in a dataframe, but if you accidentally change the dataset, it could cause problems. Using pull() is safer because it extracts the column without modifying the original dataframe.)

# Section 6: Formatting
Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

# Section 7: Learning Assessment 3

After the previous code chunk, write a bullet list given the mean, median, and standard deviation of the original random sample.

* the median is 'r round(median(pull(assessment_2, num_var)), 2)'
* the mean is 'r round(mean(pull(assessment_2, num_var)), 2)'
* the standard deviation is 'r round(sd(pull(assessment_2, num_var)), 2)'


What if I try to add a histogram?
```{r}
ggplot(plot_df, aes(x=x)) + geom_histogram()
```


